Universal Anonymous Signatures

### 2022-05-12 prism-backend/research/gsac/introduction.tex
Hotfix for bug in url hyperlink...

% What is the context for this research? Introduce previous works on this topic,
% in one paragraph. (Privacy-preserving identities, with accountability (APPI))
Successful identity representation, management, and usage are, on its own, among
the toughest problems in the Internet and digital communications at large%
\footnote{``Digital identity is one of the 21st century's biggest challenges'':
  \url{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}. Last access, May 12th, 2022.}.
Just as an illustration, think
of usernames and passwords, which end up being unmanageable as soon as we need
to start remembering a few%
\footnote{``The problem of passwords and how to deal with it'': \url{https://www.computerweekly.com/feature/The-problem-of-passwords-and-how-to-deal-with-it}. Last access,
May 12th, 2022.}; or traditional vertical PKIs, like X.509 \cite{rfc5280},
which are too rigid, and frequently require too much trust; or
horizontal PKIs, such as PGP, that are also too rigid, and are hard to manage
and scale\footnote{``What's the matter with PGP?'': \url{https://blog.cryptographyengineering.com/2014/08/13/whats-matter-with-pgp/}. Last access, May 12th, 2022}.
If, in addition, we require privacy, the scenario becomes even more
challenging. Technologies like OpenID\footnote{\url{https://openid.net/}. Last
  access, May 12th, 2022.} and OAuth\footnote{\url{https://oauth.net/}. Last
  access, May 12th, 2022.} make identity more
manageable (from the point of view of service providers) through Single Sign
On solutions. But this comes at the cost of introducing centralization points
that gain way too much knowledge beyond what is actually necessary. Holding
users accountable, or extracting utility out of their actions, is trivial in
this cases -- although that comes at the cost of barely having privacy.

>>>>

% What is the context for this research? Introduce previous works on this topic,
% in one paragraph. (Privacy-preserving identities, with accountability (APPI))
Successful identity representation, management, and usage are, on its own, among
the toughest problems in the Internet and digital communications at large%
\footnote{``Digital identity is one of the 21st century's biggest challenges'':
  \href{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}. Last access, May 12th, 2022.}.
Just as an illustration, think
of usernames and passwords, which end up being unmanageable as soon as we need
to start remembering a few%
\footnote{``The problem of passwords and how to deal with it'': \url{https://www.computerweekly.com/feature/The-problem-of-passwords-and-how-to-deal-with-it}. Last access,
May 12th, 2022.}; or traditional vertical PKIs, like X.509 \cite{rfc5280},
which are too rigid, and frequently require too much trust; or
horizontal PKIs, such as PGP, that are also too rigid, and are hard to manage
and scale\footnote{``What's the matter with PGP?'': \url{https://blog.cryptographyengineering.com/2014/08/13/whats-matter-with-pgp/}. Last access, May 12th, 2022}.
If, in addition, we require privacy, the scenario becomes even more
challenging. Technologies like OpenID\footnote{\url{https://openid.net/}. Last
  access, May 12th, 2022.} and OAuth\footnote{\url{https://oauth.net/}. Last
  access, May 12th, 2022.} make identity more
manageable (from the point of view of service providers) through Single Sign
On solutions. But this comes at the cost of introducing centralization points
that gain way too much knowledge beyond what is actually necessary. Holding
users accountable, or extracting utility out of their actions, is trivial in
this cases -- although that comes at the cost of barely having privacy.
